Proportional multi-state multiple-cohort life table model

### 2018-04-05 MSLT/MSLTdoc.Rmd
Code

####Data for example

@@

>>>>

####Data for example (CHANGE TO ENGLISH DATA, MAY NOT BE AN EXAMPLE, BUT HAVE THE DATA FOR THE CASE STUDIES (NEED TO PREPARE: LONDON, SAO PABLO, DELHI, ACCRA, LOS ANGELES, EDINBURGH)). DATA AVAILABILITY FROM GBD AT WHAT LEVEL?

@@

####Data preparation

The following code applies to the data used as an exmaple here. #6 transforms upper cases to lower cases in the sex variable. #7 and #8 is used to rename mortality_rate to mx (used in life table language). #9 is used to replace male and female in the exposure data to males and females to facilitate combination of data sets.

```{r, echo=TRUE}
#6
idata$sex <- tolower(idata$sex)
#7
idata$mx <- idata$mortality_rate
#8
idata$mortality_rate <- NULL
#9
edata$sex[edata$sex=="male"] <- "males"
edata$sex[edata$sex=="female"] <- "females"
```

```{r, echo=TRUE}
##### Create new variable for 5_year population (age cohorts). Depends on the age-cohorts of interest (5-yrs here)

idata$five_year_population <- NA
start_index <- 3
index <- 1
end_index <- 4
for (i in 1:20){
  if (i == 1)
    index <- 1
  else 
    index <- ((i - 1)  * 5) + 1
  if (index == 96){
    end_index <- 5
  }
  cat("population sum ", start_index, "start index ", index, " and end index ", index + end_index, "\n")
  idata$five_year_population[start_index] <- sum(idata$population[index:(index + end_index)])
  start_index <- start_index + 5
}

end_index <- 4
start_index <- 104

for (i in 1:20){
  if (i == 1)
    index <- 102
  else
    index <- (((i - 1)  * 5) + 1) + 101
  if (index == 197){
    end_index <- 5
  }
  cat("population sum ", start_index, "start index ", index, " and end index ", index + end_index, "\n")
  idata$five_year_population[start_index] <- sum(idata$population[index:(index + end_index)])
  start_index <- start_index + 5
}

```
